Trends in Work-related Injury Frequency Rate in Canada

### 2023-04-17 outputs/paper/paper.qmd
update paper

# Read inputs
cleaned_data <- read_csv(here::here("inputs/data/cleaned_data.csv"))

@@

This report utilizes data of injury statistics in Canada by industry sector from 2008 to 2020 obtained from the Open Government Data of Statistics Canada [@citeSC] and used programming language R [@citeR] to build models and analyze trends. The estimand of this report is work-related injury frequency rate, which is measured by injuries (disabling, fatal and minor) per one million hours worked. This paper delves into the overall trend of injury frequency rate in Canada by industry using multiple linear regression model. It was found that there was an overall downward trend in the frequency of injuries over time, with the decline most pronounced in maritime operations. Particularly, it is closely related to the proportion of outdoor workers in the industry.

@@

The original dataset contains 317 observations and 16 variables with all kinds of information about injury statistics and rates. This report wants to focus on exploring the trend of injury rate and investigating the possible factors that may affect injury rate. Thus, I will be interested in the variables "Year", "Industry", and "Injury frequency rate". R [@citeR], and R packages "tidyverse" [@citetidyverse], "dplyr" [@citedplyr], and "kableExtra" [@citekableExtra] are utilized to create an extract of the cleaned dataset (@tbl-dataextract).

@@

Prior to constructing the model, the dataset is split into the training set and the testing set with a proportion of 8:2. The training set is used to build the multiple linear regression models, and the testing set is used to test the accuracy and unbiasedness of the model. R package "tidymodels"[@citetidymodels] is used to split the dataset.

@@

@@

```{r}
# display the summarized table
summary_table %>%
  kable(
    caption = "Model Coefficients and 95 percent Confidence Interval",
col.names=c(" ", "Coefficients", "Confidence Interval Lower Bound", "Confidence Interval Upper Bound"),
linesep = "", digits = 1, booktabs=TRUE) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "12em")

@@

@@

## First discussion point

## Second discussion point

## Third discussion point

@@

@@

R package "modelsummary"[@citemodelsummary] helps to display the coefficients of the two models as well as the result of a series of tests to compare which model performs better.

$R^2$ measures how well the model explains its response variable's variation. If $R^2$ is low, it indicates that the model doesn't fit the data well. By @tbl-tabletest, in Model 1, 84.5% of the variability is explained, and in Model 2, 87.4% of the variability is explained. Both models demonstrate a pretty high $R^2$ value.

>>>>

# Read inputs
cleaned_data <- read_csv(here::here("outputs/data/cleaned_data.csv"))

@@

This report utilizes data of injury statistics in Canada by industry sector from 2008 to 2020 obtained from the Open Government Data of Statistics Canada [@citeSC] and used programming language `R` [@citeR] to build models and analyze trends. The estimand of this report is work-related injury frequency rate, which is measured by injuries (disabling, fatal and minor) per one million hours worked. This paper delves into the overall trend of injury frequency rate in Canada by industry using multiple linear regression model. It was found that there was an overall downward trend in the frequency of injuries over time, with the decline most pronounced in maritime operations. Particularly, it is closely related to the proportion of outdoor workers in the industry.

@@

The original dataset contains 317 observations and 16 variables with all kinds of information about injury statistics and rates. This report wants to focus on exploring the trend of injury rate and investigating the possible factors that may affect injury rate. Thus, I will be interested in the variables "Year", "Industry", and "Injury frequency rate". `R` [@citeR], and R packages `tidyverse` [@citetidyverse], `dplyr`[@citedplyr], and `kableExtra` [@citekableExtra] are utilized to create an extract of the cleaned dataset (@tbl-dataextract).

@@

Prior to constructing the model, the dataset is split into the training set and the testing set with a proportion of 8:2. The training set is used to build the multiple linear regression models, and the testing set is used to test the accuracy and unbiasedness of the model. R package `tidymodels` [@citetidymodels] is used to split the dataset.

@@

Model @eq-bayes is eventually selected that better demonstrates the correlation between year, industry, and the injury frequency rate in Canada. @fig-result presents a visualization of this multiple linear regression model, where each line represents the trend of injury frequency rate over time for a specific industry. The figure shows that injury frequency rate generally decreases as the year increases, indicating an improvement in workplace safety over time. 
Additionally, we can see that different industries have varying injury frequency rates, suggesting that industry type is also a significant factor in workplace safety.

@@

@tbl-sum displays the coefficients of the predictor variables in Model @eq-bayes. The model uses year 0 and the Air Transportation industry as the reference point and includes an interaction term between year and Air Transportation. The model sets a strict minimum value of 2008 for the "Year" variable. To estimate the injury frequency rate in industries other than Air Transportation, we need to consider the coefficients $\beta_2$ and $\beta_3$ which indicate the industry and the interaction between year and the specified industry, respectively. The coefficient values for these variables can be found in @tbl-sum under the "Coefficients" column.

```{r}
#| label: tbl-sum
#| tbl-cap: Model Coefficients and 95 percent Confidence Interval
# display the summarized table
summary_table %>%
  kable(
col.names=c(" ", "Coefficients", "Confidence Interval Lower Bound", "Confidence Interval Upper Bound"),
linesep = "", digits = 1, booktabs=TRUE) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  column_spec(1, width = "18em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "12em")

@@

As @tbl-sum shows, with the exception of Banking/Banks and Broadcasting (Television, Radio, Internet), all other industries experienced a decrease in injury frequency rates. The industry with the largest decline in injury frequency rates is Long shoring/Stevedoring/Port/Harbour Operations/Pilotage, with a reduction of 9.7 for every one unit increase in the "year" variable. After Long shoring/Stevedoring/Port/Harbour Operations/Pilotage, the industries with the second fastest decline in injury frequency rates are Water Transportation (Shipping and Ferries) and Energy/Mining/Mineral Processing. For every one unit increase in the "year" variable, their estimated injury frequency rates decreased by 4.2. On the other hand, Banking/Banks and Broadcasting (Television, Radio, Internet) have demonstrated the lowest decline in injury frequency rates over time. Specifically, as the "Year" variable increases by 1, the estimated injury frequency rates remain relatively stable in these sectors. While Long shoring/Stevedoring/Port/Harbour Operations/Pilotage had the highest estimated injury frequency rate earlier in 2008, the situation has changed over time. As of the end of 2020, the Postal Services/Postal Contractors industry has surpassed them, becoming the industry with the highest estimated injury frequency rate.

@@

## Trends in injury frequency rate by year

In @sec-results, we have talked about the outcome of the model, which is that time is the main factor decreasing the work-related injury frequency rate in Canada. Between 2008 and 2020, the injury frequency rate has decreased from 30.03 to 17.03 for 13. This could be due to the implementation of stricter safety regulations and guidelines in the workplace. In Canada, the Occupational Health and Safety (OHS) regulations have been in place since the 1970s and are updated annually since 2006 to keep up with new technologies and hazards [@cite2]. These regulations aim to ensure that employers provide a safe working environment for their workers, and that employees are trained to recognize and mitigate potential hazards and risks. Over the years, the regulations have evolved to address emerging issues and promote safe work practices.

Another contributing factor to the decline in work-related injuries in Canada is the increase in technology and automation in the workplace. With advancements in technology, many of the physically demanding jobs that were once commonplace have been automated, leading to a reduction in physical injuries in the workplace [@cite3]. This shift towards automation has also led to an increase in the demand for workers with technological skills, leading to a decline in physical and manual labour jobs [@cite4].

However, despite the decline in work-related injuries, there are potential problems that may arise as a result. For example, the decrease in work-related injuries may lead to complacency in the workplace, where employees may become less vigilant about safety protocols. Additionally, the decrease in work-related injuries may also lead to a lack of attention and resources towards workplace safety, as some employers may view it as less of a priority.

Even with the advancements in technology and automation, there are still potential hazards and risks that need to be addressed. Regular safety audits and risk assessments can help identify potential hazards and mitigate them before they become a problem. Employers should also provide regular training and education to their employees to ensure they are aware of potential hazards and know how to properly use equipment and machinery. Finally, it's important to create a culture of safety in the workplace, where all employees are encouraged to prioritize safety and report any potential hazards or incidents. By doing so, employers can ensure that their employees are working in a safe and healthy environment, while also reducing the risk of work-related injuries and accidents.

## The role of industry

After analyzing the decrease in injury frequency rates across various industries, our findings show that Long shoring/Stevedoring/Port/Harbour Operations/Pilotage has experienced the highest rate of decrease in injury frequency rate, followed by Water Transportation (Shipping and Ferries) and Energy/Mining/Mineral Processing. However, Banking/Banks and Broadcasting (Television, Radio, Internet) have relatively stable injury frequency rates. This disparity suggests that certain industries prioritize mitigating work-related hazards more than others.

For example, despite ranking first in injury frequency rate in 2008, Long shoring/Stevedoring/ Port/Harbour Operations/Pilotage has shown a significant decrease in injury frequency rate over the years. This improvement can be attributed to the implementation of strict safety regulations and protocols and the adoption of new technologies to reduce manual labor. In contrast, the relatively stable injury frequency rates in Banking/Banks and Broadcasting (Television, Radio, Internet) could indicate a lack of prioritization in implementing measures to mitigate work-related injuries. While these industries are generally safe, they can still lead to injuries such as musculoskeletal disorders caused by prolonged sitting and computer use.

@@

The paper delves into injury frequency rates in industries under federal jurisdiction in Canada. However, it acknowledges that the data may not accurately reflect the true incidence and severity of occupational injuries in Canada, as it only considers a subset of the workforce. Therefore, the findings must be interpreted with caution when extrapolated to the broader population. To address the limitation of the survey methodology, future research could include data from provincially regulated workplaces and industries not classified as falling under federal jurisdiction to provide a more comprehensive analysis of work-related injuries in Canada.

This paper analyzed how injury frequency rate in Canada is affected by time and different industries. However, injury frequency rate is only an aspect of work-related injury. Other aspects of work-related injury include the severity of injuries, the types of injuries, and the long-term impacts on the affected workers. Future research could explore these variations and provide a more comprehensive understanding of work-related injuries in Canada.

@@

R package `modelsummary` [@citemodelsummary] helps to display the coefficients of the two models as well as the result of a series of tests to compare which model performs better.

$R^2$ measures how well the model explains its response variable's variation. If $R^2$ is low, it indicates that the model doesn't fit the data well. By @tbl-tabletest, in Model 1, 81.7% of the variability is explained, and in Model 2, 93.2% of the variability is explained. Both models demonstrate a pretty high $R^2$ value.
